---
title: ""
output:
  html_document:
    theme: cosmo
params: 
  project_name: NA
  project_background: NA
  decision_comment: NA
  n_rows: NA
  n_cols: NA
  n_numeric: NA
  n_categorical: NA
  data_structure_numeric: NA
  data_structure_integer: NA
  data_structure_factor: NA
  eda_plots: NA
  correlation_plot: NA
  mcf: NA
  mcf_rate: NA
  nvz: NA
  lcf: NA
  stand_vars: NA
  norm_vars: NA
  trans_vars: NA
  trans_method: NA
  categorical_vars: NA
  encoding_method: NA
  na_imputation_method_num: NA
  na_imputation_method_cat: NA
  outlier_sd_range: NA
  outlier_imputation_method: NA
  data_structure_numeric_clean: NA
  data_structure_integer_clean: NA
  data_structure_factor_clean: NA
  target_variable: NA
  variable_names: NA
  considered_models: NA
  algorithm_names: NA
  holdout_ratio: NA
  hp_search_method: NA
  hp_validation_method: NA
  hp_validation_times: NA 
  var_validation_method: NA
  var_validation_times: NA 
  rfe_value: NA
  evaluation_criteria: NA
  model_highest: NA
  value_highest: NA
  model_final: NA
  final_kpi1_name: NA
  final_kpi1_value: NA
  final_kpi2_name: NA
  final_kpi2_value: NA
  comparison_plot1: NA
  comparison_plot2: NA
  model_plots1: NA
  model_plots2: NA
  importance_plots: NA
  shapley_plots1: NA
  shapley_plots2: NA
  shapley_case1: NA
  shapley_case2: NA
---

## `r params$project_name ` - Modeling Report

*** 

### <b> 1. Background </b>

`r params$project_background`

&nbsp;

### <b> 2. Dataset </b>

The data set consists of <b> `r params$n_rows` observations </b> and <b> `r params$n_cols` variables </b>. In total, <b> `r params$n_numeric` variables </b> have a <b> metric scale level </b>. <b> `r params$n_categorical` Variables </b> are characterized by a <b> categorical scale level </b>.

## {.tabset .tabset-fade}

### Numerical Variables

```{r, results='asis',echo=FALSE}
params$data_structure_numeric%>% 
  knitr::kable()  %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), fixed_thead = T) %>%
  kableExtra::scroll_box(height = "200px")

```

### Integer Variables

```{r, results='asis',echo=FALSE}
params$data_structure_integer %>% 
  knitr::kable()  %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), fixed_thead = T) %>%
  kableExtra::scroll_box(height = "200px")

```

### Factor Variables

```{r, results='asis',echo=FALSE}
params$data_structure_factor%>% 
  knitr::kable()  %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), fixed_thead = T) %>%
  kableExtra::scroll_box(height = "200px")

```

##

&nbsp;

### <b> 3. Data Pre-Processing </b>

In the next step, methods were applied to bring the data set into a suitable format for the intended modelling.

---

#### 3.1 Explorative Data Analysis

A comprehensive, <b> explorative data analysis </b> was carried out to decide on necessary preprocessing measures. The primary objective of this analysis was to illuminate the relationships between the <b> target variable `r params$target_variable` </b> and other variable in the dataset. The following figure serves as an illustrative excerpt of the analysis, visualizing the <b> correlation matrix </b> of all metric variables and the target variable:

```{r, results='asis', echo=FALSE}

print(tagList(params$correlation_plot))

```

#### 3.2 Variable Transformation

On the basis of the findings, <b> variables </b> had been eliminated for which <b> no sufficient explanatory contribution </b> could be assumed. In addition, to ensure model quality, variables were removed that were characterized by the following properties:

`r ifelse(params$mcf == TRUE, paste("- [x] Aufweisen einer Korrelation >=", params$mcf_rate, "mit einer anderen Variablen"),"XXX")`
`r ifelse(params$lcf == TRUE,"- [x] Abbildung einer Linearkombination ander Variablen","XXX")`
`r ifelse(params$nvz == TRUE,"- [x] Aufweisen einer Varianzstreuung von (nahezu) 0","XXX")`

The exclusion served the preventive <b> avoidance of falsifications and disturbances </b> within the modelling, which could result from the inclusion of variables with corresponding properties. The following variables were included for the further procedure:

##  {.tabset .tabset-pills}

```{r, results='asis', echo=FALSE}

for(y in 1:length(params$eda_plots)){
  library(shiny)
  cat("###", as.character(params$variable_names[y]), '<br>', '\n')
  
  print(tagList(params$eda_plots[[y]]))
  
  cat('\n', '<br>', '\n\n')
  
}
  

```

#

<div style="margin-top: -4em">

Due to the different scales of the metric variables included, the following <b> transformation procedures </b> were applied:

`r ifelse(length(params$stand_vars) > 0, paste("[x] <b> Standardisierung </b> von <i> ",paste(params$stand_vars, collapse =", ")," </i>"), "")`
`r ifelse(length(params$norm_vars) > 0, paste("[x] <b> Normalisierung </b> von <i> ",paste(params$norm_vars, collapse =", ")," </i>"), "")`
`r ifelse(length(params$trans_vars) > 0, paste("[x] <b> ",params$trans_method,"-Transformation </b> von <i> ",paste(params$trans_vars, collapse =", ")," </i>"), "")`

Included, <b> categorical variables </b> `r ifelse(length(params$categorical_vars)>0, paste("- <i> ",params$categorical_vars," </i> -"),""")` were in turn converted using the <b> `r params$encoding_method` encoding</b> approach to <b> binary variables </b>. Missing <b> metric data points </b> were `r ifelse(params$na_imputation_method_num != "Delete", paste("replaced by the <b> ", params$na_imputation_method_num, " </b>"), "removed")` and <b> categorial data points </b> `r ifelse(params$na_imputation_method_cat != "Delete", paste("by the <b> ", params$na_imputation_method_cat, " </b> replaced"), "removed")`. `r ifelse(params$outlier_imputation_method != "Keep", paste("Furthermore, for all variables included, a professional <b> treatment of 'outliers' </b> was undertaken. All values with a distance of more than 1.5 interquartile distances to the 25% or 75% quartile were replaced by the corresponding <b> ", params$outlier_imputation_method, "</b>."),"")`. 

</div>

---

The following table shows the essential properties of the data set after the defined preprocessing measures have been carried out:

## {.tabset .tabset-fade}

### Numerical Variables

```{r, results='asis',echo=FALSE}
params$data_structure_numeric_clean%>% 
  knitr::kable()  %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), fixed_thead = T) %>%
  kableExtra::scroll_box(height = "200px")

```

### Integer Variables

```{r, results='asis',echo=FALSE}
params$data_structure_integer_clean %>% 
  knitr::kable()  %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), fixed_thead = T) %>%
  kableExtra::scroll_box(height = "200px")

```

### Factor Variables

```{r, results='asis',echo=FALSE}
params$data_structure_factor_clean%>% 
  knitr::kable()  %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), fixed_thead = T) %>%
  kableExtra::scroll_box(height = "200px")

```

##

&nbsp;


### <b> 4. Modeling </b>

The adjusted data set was subsequently transferred into a <b> structured training pipeline </b> in which various modelling options were simulated and evaluated. For later evaluation of model quality and stability, <b> `r params$holdout_ratio` % </b> of the data set was defined as <b> holdout set </b>, which was excluded from the training process. Furthermore, <b> validation loops </b> were integrated within the pipeline for <b> variable and hyperparameter selection </b>.
---

#### 4.1 Modeling Approach

The following algorithms were considered on the basis of the requirement horizon resulting from the question.
 
```{r, echo=FALSE, results="asis"}
for (i in 1:length(params$considered_models)) {
  cat("- ",params$algorithm_names[[i]], '<br>', '\n')
}
```

The <b> `r params$hp_search_method` principle </b> was used to select the associated <b> hyperparameters </b>, in which the modeling quality for a number of `r ifelse(params$hp_search_method=="grid", "predefined", "randomly selected")` parameter combinations is evaluated one after the other. The <b> hyper parameter combinations </b> was optimized by a <b>`r as.character(params$hp_validation_times)`-fold `r toupper(params$hp_validation_method) `-validation </b> within the <i> internal validation loop </i>. <!-- Parallel to this, different combinations of the explanatory variables were tested within the <i> external validation loop </i> using <b> `r params$var_validation_times`-fold `params$var_validation_method` </b>. The optimization was done by <i> 'Recursive Feature Elimination' </i> procedure with a <b> RFE value </b> of <b> `params$rfe_value` </b>. -->

&nbsp;

### <b> 5. Model Evaluation </b>

Both <b> accuracy criteria </b> and <b> interpetibility criteria </b> were considered for the selection of the model to be <b> preferred </b>. 

----

#### 5.1 Model Performance 

The performance of all models included was assessed using the indicator <b> "`r params$evaluation_criteria`" </b>. The following figure shows the <b> dispersion of the performance values </b> within the validation loops for each algorithm. With a <b> `r params$evaluation_criteria` </b> of <b> `r params$value_highest` </b> the algorithm <b> "`r params$model_highest`" </b> has the highest average forecasting power.

<div class="row">
  <div class="col-md-6" markdown="1">
  `r params$comparison_plot1`
  </div>
  <div class="col-md-6" markdown="1">
  `r params$comparison_plot2`
  </div>
</div>

<div style="margin-top: -2em">
In order to obtain a holistic picture of the algorithm performance, the <b> distributions of the predicted values </b> were also considered. The following figures show these and the <b> residuals to the actual values </b> for the algorithms used: 
</div>

## {.tabset .tabset-pills}

```{r, results='asis', echo=FALSE}

if (length(params$model_plots1)==1) {
  
     tagList(column(width=6,params$model_plots1[[1]]),column(width=6,params$model_plots2[[1]]))
  
  } else {
  
  for(h in 1:length(params$model_plots1)){
  library(shiny)
  cat("###", as.character(params$algorithm_names[[h]]), '<br>', '\n')
  print(tagList(column(width=6,params$model_plots1[[h]]),column(width=6,params$model_plots2[[h]])))
  cat('\n', '<br>', '\n\n')
}
  
}

```

##

&nbsp;

<div style="margin-top: -3em">
----

</div>


#### 5.2 Model Interpretability

After evaluation of the performance, all trained models were evaluated with regard to <b> traceability and plausibility </b> of their prognosis. As a first indicator, the <b> general explanatory contribution </b> of the included predictors was examined. The following figure visualizes the <b> relative significance of the variables </b> included for each algorithm at an aggregated level: 

## {.tabset .tabset-pills}

```{r, results='asis', echo=FALSE}

if (length(params$importance_plots)==1) {
  
     tagList(params$importance_plots[[1]])

  } else {
  
  for(h in 1:length(params$importance_plots)){
  library(shiny)
  cat("###", as.character(params$algorithm_names[[h]]), '<br>', '\n')
  print(tagList(params$importance_plots[[h]]))
  cat('\n', '<br>', '\n\n')
  
}
  
}

```

##
 
The knowledge gained from this was expanded by including a <b> local interpretation indicator </b> - the associated <b> SHAPLEY values </b> -. <b> `r params$shapley_case1`</b> and <b> `r params$shapley_case2` </b> were selected as illustrative cases to illustrate the influence of the variables on the corresponding prognostic value:


## {.tabset .tabset-pills}

```{r, results='asis', echo=FALSE}

if (length(params$model_plots1)==1) {
  
     tagList(column(width=6,params$model_plots1[[1]]),column(width=6,params$model_plots2[[1]]))

  
  } else {
  
  for(h in 1:length(params$shapley_plots1)){
  library(shiny)
  cat("###", as.character(params$algorithm_names[[h]]), '<br>', '\n')
  print(tagList(column(width=6,params$shapley_plots1[[h]]),column(width=6,params$shapley_plots2[[h]])))
  cat('\n', '<br>', '\n\n')
}
  
}

```

##

#### 5.3 Preferred Model

After careful consideration of all models regarding accuracy and interpretability, the model <b> `r params$model_final` </b> was chosen. It had an average <b> `r params$final_kpi1_name` value</b> of <b> `r params$final_kpi1_value` </b> and a <b> `r params$final_kpi2_name` value</b> of <b> `r params$final_kpi2_value` </b>.

</b> 

`r params$decision_comment`

